IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-08 ms.tex
I added some discussion/references of condensates and corrected the rotation period for 2MASS 0835.

Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
Their temperatures are cool enough that they span condensation points of many cloud-producing  compounds.

The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.

@@

We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.

\begin{table*}
\begin{center}
\begin{tabular}{ccccr}
Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ \\
-- & (hr) & -- & -- & (K) \\
\hline \hline
2MASS J1821+14010 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} \\
2MASS J0835-019 & 9 & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} \\
\end{tabular}
\end{center}
\tablenotetext{a}{\citet{metchev2015weatherII}.}
\tablenotetext{b}{\citet{gagne2015banyan7}.}
\tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}

\end{table*}

@@

>>>>

Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
Their temperatures are cool enough that they span condensation points of many cloud-producing  compounds including H$_2$O, MgSiO$_3$, Mg$_2$SiO$_4$ and Fe \citep{marley2015rev}.

The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
Brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.

@@

We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable with a period of 9 hr.

Both brown dwarfs' effective temperatures in Table \ref{tab:bdProp} are near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$ \citep{marley2015rev} so these are viable candidates for clouds in their atmospheres.

\begin{table*}
\begin{center}
\caption{Brown Dwarf Properties}\label{tab:bdProp}
\begin{tabular}{ccccrr}
Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ &  $v$ sin($i$) \\
-- & (hr) & -- & -- & (K) & (km/s) \\
\hline \hline
2MASS 1821 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} & 28.85 $\pm$ 0.16\tablenotemark{d}\\
2MASS 0835 & 3.1\tablenotemark{d} & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} & 14.18 $\pm$ 0.43\tablenotemark{d} \\
\end{tabular}
\end{center}
\tablenotetext{a}{\citet{metchev2015weatherII}.}
\tablenotetext{b}{\citet{gagne2015banyan7}.}
\tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}
\tablenotetext{d}{\citet{blake2010nirspecVS}}
\tablenotetext{e}{\citet{koen2004ibandBD}}
\end{table*}

@@

We observed two brown dwarfs of spectral type L4-L5: 2MASS 1821 and 2MASS 0835.
These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems.
After fitting sinusoids to both of the time series, we find that the
